Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-01-29 revisionMemo/rev1.tex
CD attempts

		TO DO: The reviewer is correct in that our paper addresses the majority of IR scholarship that misuses GLM approaches for dyadic data. We have rewritten these sentences in the following way: In practice, such strategies remain problematic because they do not directly address the fundamental data generating process but instead seek to correct for dependence while using a baseline model that makes strong assumptions about the independence of observations in the DGP. While corrections such as X and Y are beneficial at times for A and B, these approaches remain only partially useful, and do not sufficiently capture third-order dependencies that organically arise from dyadic data. 

@@

		TO DO: We have revised this opening statement to clarify our position. 

>>>>

		TO DO/CD: The reviewer is correct in that our paper addresses the majority of IR scholarship that misuses GLM approaches for dyadic data. We have rewritten these sentences in the following way: In practice, such strategies remain problematic because they do not directly address the fundamental data generating process but instead seek to correct for dependence while using a baseline model that makes strong assumptions about the independence of observations in the DGP. While corrections such as X and Y are beneficial at times for A and B, these approaches remain only partially useful, and do not sufficiently capture third-order dependencies that organically arise from dyadic data. 

@@

		TO DO/CD: We have revised this opening statement to clarify our position. Max: I'm wondering if we should combine this with the Q above or is R1's question here distinct enough?

### 2020-01-29 revisionMemo/rev2.tex
assign one more task
started response to reviewer comment on appendix c tutorial
CD attempts

@@

	\item The paper emphasizes on the importance of estimating the random effects for theory building and hypothesis test. A longer elaboration and illustration of this point would be very helpful.

@@

@@

@@

>>>>

		TODO/CD: We agree with this suggestion. We have now emphasized the importance of developing theory in our discussion of the AME and Oracle comparison (p. X), as well as in the conclusion of our paper (p.Y).

@@

	\item The paper emphasizes the importance of estimating the random effects for theory building and hypothesis test. A longer elaboration and illustration of this point would be very helpful.

@@

		TODO/CD: I think this comment and the above comment are essentially the same. We could even cite our JOP as an example of incorporating theory?  Perhaps other new-ish net paper as well?

@@

		TO DO/CD: We selected our cases based on a few criteria. We focus on studies that are explicitly about International Relations, were published in the last 10 years, and were published in a top ranking general political science outlet (for consistency in editorial standards and reviews, we also decided to focus on one journal, the APSR). We hope that these three criteria ensure that our paper is readable and interpretable to an applied audience. In addition, we selected studies that could help illustrate different key components of the AME approach (Max, more here on each?).  While we agree with the reviewer that further replications would effectively demonstrate the benefits of the AME, they are beyond the scope of this paper at this time. (CD: Should we also mention something like 'in consultation with the editor, we believe they are beyond the scope....") 

@@

		The reviewer raises a valid point. We have expanded our tutorial in Appendix C, particularly in giving more detail and concrete examples when it comes to formatting the data, which may represent the biggest hurdle for some users. We also...
